
\newglossaryentry{disguise}
{
    name=disguise,
    description={a shape-shifting technology invented by the union mimicking the ability of one of their specie.}
}

\newglossaryentry{dffc}{
    name={Declaration of Foundation of the Federation of Continents (The)},
    description={The treaty that formed the word government known as the Federation of Continents, a federation of all the continents nations. also called Federation Treaty as a reference to the Union Treaty}
}

\newglossaryentry{europe}{
    name={Europe},
    description={The nation created by the fusion of the ex-nation of the EU and other nation on the european continent}
}

\newglossaryentry{federationt}{
    name={Federation Treaty},
    description={see Declaration of Foundation of the Federation of Continents}
}

\newglossaryentry{federation}{
    name={Federation of Continents},
    description={The world federation of all continents nations on earth.}
}

\newglossaryentry{fsp}{
    name={Federation Space Program},
    description={The space program of the Federation of Continents}
}

\newglossaryentry{ftl}{
    name=FTL,
    description={Faster Than Light}
}

\newglossaryentry{ijpl}{
    name={International Jet Propulsion Laboratory},
    description={The successor of the NASA's Jet Propulsion Laboratory, attached to the Federation Space Program}
}

\newglossaryentry{mic}{
    name={Massacre of the International Convention},
    description={The event which happened in the first International Convention of the United Nation in 2023 (a big reunion of all representative from the 200+ nations on earth), a series of terrorist attacks from North Korea killed 2000 people, more than half of all the heads of states of the earth died in this attack. This attack directly caused the international efforts to unionize.}
}

\newglossaryentry{np}{
    name={New Paris},
    description={The capital of Europe, its exact geographic position is purposely not stated, somewhere between Belgium, France, Germany, Italy and Switzerland. Named after the former capital of France and most populated city of the UE, Paris}
}

\newglossaryentry{ut}{
    name={Union Treaty},
    description={The treaty which formed Europe out of the then European Union, following the events of the Massacre of the International Convention.}
}

\newglossaryentry{union}{
    name={Union (The)},
    description={The group of highly advanced alien species that formed an alliance spanning across 80 to 120 LY.}
}

\newglossaryentry{uc}{
    name={Union Central},
    description={The central political capital of The Union.}
}

\newglossaryentry{us}{
    name={Union Standard},
    description={The language spoken in the Union}
}

\newglossaryentry{es}{
    name={Earth Standard},
    description={The language spoken on Earth (a dialect of English)}
}